Spike spectra for recurrences

### 2022-11-16 Manuscript/entropy-1919488  proof/entropy-1919488.tex
links to Julia and Matlab published repos

\dataavailability{The study that we present here is available as a fully reproducible code base
``repository will be published and cited here, when accepted'' and the method
will be available in the Julia language, ``package will be published and cited here, 
when accepted'' and as a MATLAB\textsuperscript{\textregistered} toolbox 
``Toolbox will be published and cited here, when accepted''.}

>>>>

\dataavailability{The study that we present here is available as a fully reproducible code base
**Repository will be published and cited here, when accepted** and the method
will be available in the Julia language (https://zenodo.org/record/7328513#.Y3Vb4VLMJqw) and as a MATLAB\textsuperscript{\textregistered} toolbox 
(https://zenodo.org/record/7328499#.Y3Vb91LMJqw).}

### 2022-11-16 Manuscript/inter_spike_manuscript_mdpi.tex
links to Julia and Matlab published repos

\dataavailability{The study that we present here is available as a fully reproducible code base
**Repository will be published and cited here, when accepted** and the method
will be available in the Julia language **Package will be published and cited here, 
when accepted** and as a MATLAB\textsuperscript{\textregistered} toolbox 
**Toolbox will be published and cited here, when accepted**.}

>>>>

\dataavailability{The study that we present here is available as a fully reproducible code base
**Repository will be published and cited here, when accepted** and the method
will be available in the Julia language (https://zenodo.org/record/7328513#.Y3Vb4VLMJqw) and as a MATLAB\textsuperscript{\textregistered} toolbox 
(https://zenodo.org/record/7328499#.Y3Vb91LMJqw).}
